\section{First Last}\label{first-last}

\subsection{Software Development
Engineer}\label{software-development-engineer}

\noindent\rule{\linewidth}{0.5pt}

\justifying

\faIcon{map-marker-alt} Chicago, IL \faEnvelope{} firstlast@gmail.com
\faPhone{} (123) 456-7890 \faIcon{linkedin} firstlast \faIcon{github}
first-last

\noindent\rule{\linewidth}{0.5pt}

February 7, 2025

PLACEHOLDER COMPANY

Dear Hiring Manager,

I am excited to apply for the freelance Programmer opportunity at
Outlier. My experience in software development, particularly in Python
and large language model interaction, aligns perfectly with the
requirements of this role. I am confident I can contribute significantly
to training your AI models.

In my previous role developing a custom job posting board, I designed
and implemented a data pipeline that successfully integrated with
Google's Gemini API to process and classify job postings, resulting in a
80\% reduction in time required for job applications and ensuring only
relevant opportunities are presented to users. This involved handling
the unreliability of the Gemini API, requiring the implementation of
robust error handling and exponential backoff strategies to maintain a
consistent data flow, mirroring the challenges inherent in training
complex AI models.

Key highlights of my qualifications include:

\begin{itemize}
\tightlist
\item
  \textbf{API Integration and Data Processing:} Successfully integrated
  with multiple third-party APIs (Indeed, Glassdoor, ZipRecruiter, and
  Google Gemini), processing large volumes of data and implementing
  robust error handling resulting in a highly reliable data pipeline.
\item
  \textbf{Large Language Model Interaction:} Developed and deployed a
  system leveraging Google Gemini's large language model to classify job
  postings and generate tailored application materials, demonstrating
  proficiency in interacting with and interpreting outputs from LLMs.
\item
  \textbf{Python and Flask Development:} Designed and developed a
  full-stack web application using Python, Flask, and PostgreSQL,
  showcasing my ability to build and deploy functional, scalable
  applications.
\end{itemize}

Outlier's mission of improving AI models through human feedback
resonates deeply with my passion for leveraging technology to solve
complex problems. The opportunity to contribute to the training of
generative AI models, particularly those focused on code generation,
excites me, given my substantial experience with different programming
languages and my demonstrable ability to work with complex APIs and
large language models.

I am eager to discuss how my skills and experience can contribute to
Outlier's success. I welcome the opportunity to further discuss my
application at your earliest convenience.

Sincerely,\\
First Last
